---
title: "Homework 04: Statistical inference"
subtitle: "Due: Friday, March 26 11:59pm ET"
author: "Navya Belavadi"
date: "03-21-2021"
output:
  pdf_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, 
                      warning = FALSE, comment = "#>", highlight = TRUE)
set.seed(37073)
```

# Packages

```{r packages}
library(tidyverse)
library(infer)
```

# Data

```{r load_data}
gifted <- read_csv("https://www.openintro.org/data/csv/gifted.csv")
```

# Exercises

## Exercise 1
The sample size Gallup took in the 2016-2017 nationwide study was 337,690.

## Exercise 2
The quantity 11.5% represents the percent of the national population that was told by a doctor or a nurse that they have diabetes during 2016-2017. The quantity 10.8% represents the percent of the national population that was told by a doctor or a nurse that they have diabetes during 2008-2009.



## Exercise 8

```{r ex_8}
gifted %>% 
  pivot_longer(cols      = edutv:cartoons, 
               names_to  = "tv_type", 
               values_to = "tv_hours")
```



# References

Gallup, I. (2018). Diabetes Rates Rise in 18 States in Past Decade. 
Gallup.com. Retrieved from 
https://news.gallup.com/poll/243911/diabetes-rates-rise-states-past-decade.aspx
