---
title: "Homework 04: Statistical inference"
subtitle: "Due: Friday, March 26 11:59pm ET"
author: "Navya Belavadi"
date: "03-21-2021"
output:
  pdf_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, 
                      warning = FALSE, comment = "#>", highlight = TRUE)
set.seed(37073)
```

# Packages

```{r packages}
library(tidyverse)
library(infer)
```

# Data

```{r load_data}
gifted <- read_csv("https://www.openintro.org/data/csv/gifted.csv")
```

# Exercises

## Exercise 1
The sample size Gallup took in the 2016-2017 nationwide study was 337,690.

## Exercise 2
The quantity 11.5% represents the percent of the national population that was told by a doctor or a nurse that they have diabetes during 2016-2017. The quantity 10.8% represents the percent of the national population that was told by a doctor or a nurse that they have diabetes during 2008-2009.

## Exercise 3
The 95% confidence interval for the proportion of adult individuals that have diabetes is 11.3% to 11.7%, which can be determined because the margin of sampling error was +/- 0.2 and the point estimate was 11.5%. 

## Exercise 4
The 95% confidence interval for the proportion of adults with diabetes in Alaska is 4.9% to 11.9%, due to the margin of sampling error being +/- 3.5 and the point estimate being 8.4%.

## Exercise 5
```{r}
insurance <- tibble(claims = rep(c("met", "unmet"), times = c(55, 20)))

insurance %>%
  prop_test(response = claims, success = "met", conf_int = FALSE, alternative = "less", z = TRUE, p = 0.9)
```

The point estimate is 55/75 = 0.73333, null hypothesis is p = 0.9, and the alternative hypothesis is p < 0.9. Since the p value, 7.499e-7, is less than the significance level of 0.05, the null hypothesis can be rejected. Therefore, there is sufficient evidence that the consumer group is right, and that the true proportion of claims is less than 90%.

## Exercise 6
10,000 replications for 6

## Exercise 7
```{r}
bootstrap_mean <- gifted %>%
  specify(response = count) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean") %>%
  get_ci(level = 0.98)
bootstrap_mean
```
This output means that one can be 98% confident that the mean number of months until gifted children from the specified city can count to 10 is between 29 and 32.333. 


## Exercise 8

```{r ex_8}
gifted %>% 
  pivot_longer(cols      = edutv:cartoons, 
               names_to  = "tv_type", 
               values_to = "tv_hours")
```





# References

Gallup, I. (2018). Diabetes Rates Rise in 18 States in Past Decade. 
Gallup.com. Retrieved from 
https://news.gallup.com/poll/243911/diabetes-rates-rise-states-past-decade.aspx
