---
title: "Homework 04: Statistical inference"
subtitle: "Due: Friday, March 26 11:59pm ET"
author: "Navya Belavadi"
date: "03-21-2021"
output:
  pdf_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, 
                      warning = FALSE, comment = "#>", highlight = TRUE)
set.seed(37073)
```

# Packages

```{r packages}
library(tidyverse)
library(infer)
```

# Data

```{r load_data}
gifted <- read_csv("https://www.openintro.org/data/csv/gifted.csv")
```

# Exercises

## Exercise 1
The sample size Gallup took in the 2016-2017 nationwide study was 337,690.

## Exercise 2
The quantity 11.5% represents the percent of the national population that was told by a doctor or a nurse that they have diabetes during 2016-2017. The quantity 10.8% represents the percent of the national population that was told by a doctor or a nurse that they have diabetes during 2008-2009.

## Exercise 3
The 95% confidence interval for the proportion of adult individuals that have diabetes is 11.3% to 11.7%, which can be determined because the margin of sampling error was +/- 0.2 and the point estimate was 11.5%. 

## Exercise 4
The 95% confidence interval for the proportion of adults with diabetes in Alaska is 4.9% to 11.9%, due to the margin of sampling error being +/- 3.5 and the point estimate being 8.4%.

## Exercise 5
```{r}
insurance <- tibble(claims = rep(c("met", "unmet"), times = c(55, 20)))

insurance %>%
  prop_test(response = claims, success = "met", conf_int = FALSE, alternative = "less", z = TRUE, p = 0.9)
```

The point estimate is 55/75 = 0.73333. 

## Exercise 6



## Exercise 8

```{r ex_8}
gifted %>% 
  pivot_longer(cols      = edutv:cartoons, 
               names_to  = "tv_type", 
               values_to = "tv_hours")
```

10,000 replications for 6




# References

Gallup, I. (2018). Diabetes Rates Rise in 18 States in Past Decade. 
Gallup.com. Retrieved from 
https://news.gallup.com/poll/243911/diabetes-rates-rise-states-past-decade.aspx
