---
title: "Homework 04: Statistical inference"
subtitle: "Due: Friday, March 26 11:59pm ET"
author: "Navya Belavadi"
date: "03-21-2021"
output:
  pdf_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, 
                      warning = FALSE, comment = "#>", highlight = TRUE)
set.seed(37073)
```

# Packages

```{r packages}
library(tidyverse)
library(infer)
```

# Data

```{r load_data}
gifted <- read_csv("https://www.openintro.org/data/csv/gifted.csv")
```

# Exercises

## Exercise 1
The sample size Gallup took in the 2016-2017 nationwide study was 337,690 
interviews.

## Exercise 2
The quantity 11.5% represents the percent of the national population that was 
diagnosed by a doctor or a nurse that they have diabetes during 2016-2017. The 
quantity 10.8% represents the percent of the national population that was 
diagnosed by a doctor or a nurse that they have diabetes during 2008-2009.

## Exercise 3
The 95% confidence interval for the proportion of adult individuals that have 
diabetes is 11.3% to 11.7%, which can be determined because the margin of 
sampling error was +/- 0.2 and the point estimate was 11.5%. This can be 
determined using the equation confidence interval = point estimate +/- margin of
sampling error. 

With this information, it can be known with 95% confidence that the true 
proportion of adults that were told by a doctor or nurse that they have diabetes
lies between 11.3% and 11.7%. 

## Exercise 4
The 95% confidence interval for the proportion of adults with diabetes in Alaska
is 4.9% to 11.9%, due to the margin of sampling error being +/- 3.5 and the 
point estimate being 8.4%.

## Exercise 5
```{r ex_5}
insurance <- tibble(claims = rep(c("met", "unmet"), times = c(55, 20)))

insurance %>%
  prop_test(response = claims, success = "met", conf_int = FALSE, alternative = 
              "less", z = TRUE, p = 0.9)
```

The point estimate is 55/75 = 0.73333, null hypothesis is p = 0.9, and the 
alternative hypothesis is p < 0.9. Since the p value, 7.499e-7, is less than the
significance level of 0.05, the null hypothesis can be rejected. Therefore, 
there is sufficient evidence that the consumer group is right, and that the true
proportion of claims is less than 90%.

## Exercise 6
```{r ex_6}
claims <- tibble(settlement = rep(c("settled", "unsettled"), times = c(55,20)))

null_d<- claims %>%
  specify(response = settlement, success = "settled") %>%
  hypothesize(null = "point", p = 0.90) %>%
  generate(reps = 10000) %>%
  calculate(stat = "prop")
p_hat <- claims %>%
  count(settlement) %>%
  mutate(prop = n / sum(n)) %>%
  filter(settlement == "settled") %>%
  select(prop)
p_hat

null_d %>%
  get_p_value(obs_stat = p_hat, direction = "less")
```
```{r}
visualize(null_d) +
  shade_p_value(obs_stat = p_hat, direction = "less") + coord_flip() + labs(y = 
  "Count", y = "Sample Proportion")
```
After using a simulations based approach, the result was a p value of 2e-04, and
the sample statistic value is 0.7333. Since the p value is less than the 
significance level, the null hypothesis can be rejected and the same conclusion 
made that the percent of claims that are settled within 30 days is less than 90%
for the insurance company.

## Exercise 7
```{r ex_7}
bootstrap_mean <- gifted %>%
  specify(response = count) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean") %>%
  get_ci(level = 0.98)
bootstrap_mean
```
This output means that one can be 98% confident that the mean number of months 
until gifted children from the specified city can count to 10 is between 29 and 
32.333. 

## Exercise 8

```{r ex_8}
gifted <- gifted %>% 
  pivot_longer(cols      = edutv:cartoons, 
               names_to  = "tv_type", 
               values_to = "tv_hours")
d_hat <- gifted %>%
  specify(tv_hours ~ tv_type) %>%
  calculate(stat = "diff in means", order = c("cartoons", "edutv"))
boot <- gifted %>%
  specify(tv_hours ~ tv_type) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("cartoons", "edutv"))
percentile_ci <- get_ci(boot, level = 0.99)
percentile_ci
```
Based on this confidence interval, it can be seen with 99% confidence that the 
true difference between gifted children watching cartoon TV and gifted children 
watching educational TV lies in the interval between 0.743 and 1.458 in mean 
hours. Because this true mean difference will be positive, it can be concluded 
that gifted children spend more time watching cartoons than educational TV. 


## Exercise 9
A will have the largest interval -- despite A and B being the same size, A has a
confidence interval of 90% rather than 95% which B has. This lower confidence 
interval means the part of the data set that is included will be less narrow 
since the standards are not as high. B will have the second largest interval, 
and C will have the smallest because of the high p value which narrows out half 
of the data set.

## Exercise 10
Some potential consequences from a Type I error (in which a true null hypothesis
is rejected) could be that catheters that are actually safe to use would be 
discarded incorrectly or production halted (the null hypothesis should not have 
been rejected). Potential consequences from a Type II error (in which a false 
null hypothesis is failed to be rejected) is catheters which are unusable would 
continue to be used/produced (the null hypothesis should have been rejected). 

# References

Gallup, I. (2018). Diabetes Rates Rise in 18 States in Past Decade. 
Gallup.com. Retrieved from 
https://news.gallup.com/poll/243911/diabetes-rates-rise-states-past-decade.aspx
